Environmental and geographic variables are effective surrogates for genetic variation in conservation planning

### 2016-09-20 code/rmarkdown/supporting_information.Rmd
+ upgrade article deps to 3.3.1
+ assorted fixes to manuscript * rewrote some parts of article * fixed figure sizing in si

```{r, include=FALSE}
# load .rda file
try(session::restore.session('data/final/results.rda'))

@@

```{r, fig.width=15, fig.height=3, fig.cap='Climatic variation. Each panel depicts variation based on a different principle component (PC). Squares represent planning units. The color of each planning unit denotes the average PC value of pixels inside it. Planning units with more similar colors have more similar climate regimes.', echo=FALSE}
do.call(
	grid.arrange,
		append(
		llply(grep('^env\\_.*$', names(grid.DF), value=TRUE), function(x) {
			grid.FPLY$plot_title <- paste0('PC ', substr(x, nchar(x), nchar(x)))
			ggplot() +
				geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
					fill='grey85', color='grey70') +
				geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
					group='group', fill=x), color='grey10') +
				theme_classic() +
				theme(
					axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
					panel.border=element_rect(color='black', fill=NA, size=1),
					strip.background = element_rect(fill='grey20'),
					strip.text = element_text(color='white', size=5)
				) +
				coord_cartesian(
					xlim=buffered.range(grid.FPLY$long, 0),
					ylim=buffered.range(grid.FPLY$lat, 0)
				) +
				scale_fill_gradientn(name='',
					colors=brewer.pal(9, 'RdYlBu'),
					guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
				) +
				facet_wrap(~ plot_title)
		}),
		list(ncol=4)
	)
)
```

@@

```{r, echo=FALSE}
plot.spp.nmds <- function(i) {
	## prepare data
	# get vector of adaptive and neutral column names
	adapt.col <- grep(
		paste0(unique(spp.samples.DF$species)[i], '_adaptive_d'),
		names(grid.FPLY), value=TRUE, fixed=TRUE
	)
	neutral.col <- grep(
		paste0(unique(spp.samples.DF$species)[i], '_neutral_d'),
		names(grid.FPLY), value=TRUE, fixed=TRUE
	)
	# skip species if not used in analysis
	curr.FPLY <- grid.FPLY[,
		c(adapt.col, neutral.col,
		'long','lat','group'),drop=FALSE]
	curr.FPLY <- curr.FPLY[which(!is.na(curr.FPLY[[1]])),]
	curr.FPLY <- curr.FPLY %>% gather(d, value, contains('adaptive'), contains('neutral')) %>% mutate(
		d=gsub(paste0(unique(spp.samples.DF$species)[i], '_'), '', d, fixed=TRUE),
		d=gsub('_', ' ', d, fixed=TRUE)
	)
	for (j in seq_len(length(adapt.col)+length(neutral.col)))
		curr.FPLY[['d']] <- gsub(as.character(j), paste0('(', j, ')'), curr.FPLY[['d']], fixed=TRUE)
	curr.FPLY <- curr.FPLY %>% mutate(d=factor(gsub(' d(', ' (', d, fixed=TRUE)))
	# make plot
	curr.GROBS <- llply(unique(curr.FPLY$d), function(x) {
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey85', color='grey70') +
			geom_polygon(data=filter(curr.FPLY, d==x), aes_string(x='long', y='lat', 
				group='group', fill='value'), color='grey10') +
			theme_classic() +
			theme(
				axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
				panel.border=element_rect(color='black', fill=NA, size=1),
				strip.background = element_rect(fill='grey20'),
				strip.text = element_text(color='white', size=20)
			) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0),
				ylim=buffered.range(grid.FPLY$lat, 0)
			) +
			scale_fill_gradientn(name='',
				colors=brewer.pal(9, 'RdYlBu'),
				guide=guide_colorbar(ticks=element_line(color='black'),
					border=element_line(color='black'), barheight=unit(7, 'cm'))
			) + facet_wrap(~d)
	})
	do.call(grid.arrange, append(curr.GROBS, list(ncol=3)))
	invisible()
}

calc.fig.height <- function(i) {
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	n.plots <- 0 
	# count adaptive plot
	if (adapt.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
	# count neutral plot
	if (neutral.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
	# exports
	return((((n.plots-1) %/% 3)+1) * 2.5)
}

calc.fig.width <- function(i) {
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	n.plots <- 0 
	# count adaptive plot
	if (adapt.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
	# count neutral plot
	if (neutral.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
	# exports
	if (n.plots > 3) n.plots <- 3
	return((10/3) * n.plots)
}

@@

```{r, echo=FALSE, fig.width=calc.fig.width(1), fig.height=calc.fig.height(1), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each panel shows a different dimension of the variation as indicated by its title. Squares represent planning units. The color of each planning unit panel corresponds to the average ordinated values associated with individuals sampled inside it. No indiviudals of this species were found inside the gray planning units.')}
if (is.speciesPlottable(1)) plot.spp.nmds(1)
 ```

```{r, echo=FALSE, fig.width=calc.fig.width(2), fig.height=calc.fig.height(2), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(2)) plot.spp.nmds(2)
```

```{r, echo=FALSE, fig.width=calc.fig.width(3), fig.height=calc.fig.height(3), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(3)) plot.spp.nmds(3)
```

```{r, echo=FALSE, fig.width=calc.fig.width(4), fig.height=calc.fig.height(4), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(4)) plot.spp.nmds(4)
```

```{r, echo=FALSE, fig.width=calc.fig.width(5), fig.height=calc.fig.height(5), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(5)) plot.spp.nmds(5)
```

```{r, echo=FALSE, fig.width=calc.fig.width(6), fig.height=calc.fig.height(6), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(6)) plot.spp.nmds(6)
```

```{r, echo=FALSE, fig.width=calc.fig.width(7), fig.height=calc.fig.height(7), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(7)) plot.spp.nmds(7)
```

```{r, echo=FALSE, fig.width=calc.fig.width(8), fig.height=calc.fig.height(8), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(8)) plot.spp.nmds(8)
```

```{r, echo=FALSE, fig.width=calc.fig.width(9), fig.height=calc.fig.height(9), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(9)) plot.spp.nmds(9)
```

```{r, echo=FALSE, fig.width=calc.fig.width(10), fig.height=calc.fig.height(10), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(10)) plot.spp.nmds(10)
```

```{r, echo=FALSE, fig.width=calc.fig.width(11), fig.height=calc.fig.height(11), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(11)) plot.spp.nmds(11)
```

```{r, echo=FALSE, fig.width=calc.fig.width(12), fig.height=calc.fig.height(12), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(12)) plot.spp.nmds(12)
```

```{r, echo=FALSE, fig.width=calc.fig.width(13), fig.height=calc.fig.height(13), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(13)) plot.spp.nmds(13)
```

```{r, echo=FALSE, fig.width=calc.fig.width(14), fig.height=calc.fig.height(14), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(14)) plot.spp.nmds(14)
```

```{r, echo=FALSE, fig.width=calc.fig.width(15), fig.height=calc.fig.height(15), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(15)) plot.spp.nmds(15)
```

```{r, echo=FALSE, fig.width=calc.fig.width(16), fig.height=calc.fig.height(16), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(16)) plot.spp.nmds(16)
```

```{r, echo=FALSE, fig.width=calc.fig.width(17), fig.height=calc.fig.height(17), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(17)) plot.spp.nmds(17)
```

```{r, echo=FALSE, fig.width=calc.fig.width(18), fig.height=calc.fig.height(18), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(18)) plot.spp.nmds(18)
```

```{r, echo=FALSE, fig.width=calc.fig.width(19), fig.height=calc.fig.height(19), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(19)) plot.spp.nmds(19)
```

```{r, echo=FALSE, fig.width=calc.fig.width(20), fig.height=calc.fig.height(20), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(20)) plot.spp.nmds(20)
```

```{r, echo=FALSE, fig.width=calc.fig.width(21), fig.height=calc.fig.height(21), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(21)) plot.spp.nmds(21)
```

```{r, echo=FALSE, fig.width=calc.fig.width(22), fig.height=calc.fig.height(22), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(22)) plot.spp.nmds(22)
```

```{r, echo=FALSE, fig.width=calc.fig.width(23), fig.height=calc.fig.height(23), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(23)) plot.spp.nmds(23)
```

```{r, echo=FALSE, fig.width=calc.fig.width(24), fig.height=calc.fig.height(24), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(24)) plot.spp.nmds(24)
```

```{r, echo=FALSE, fig.width=calc.fig.width(25), fig.height=calc.fig.height(25), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(25)) plot.spp.nmds(25)
```

```{r, echo=FALSE, fig.width=calc.fig.width(26), fig.height=calc.fig.height(26), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(26)) plot.spp.nmds(26)
```

```{r, echo=FALSE, fig.width=calc.fig.width(27), fig.height=calc.fig.height(27), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S6 caption for conventions.')}
if (is.speciesPlottable(27)) plot.spp.nmds(27)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=(2.5*4), fig.cap='The relationship between the proportion of adaptive genetic variation secured in a prioritizaiton and the proportion of environmental variation it also secures. Points represent values associated with randomly generated prioritizations. Blue lines indicate average trends computed using a generalised linear model with a logit link. Each panel shows data for a different species.'}
# format data
curr.DF <- env.surrogacy.DF %>% filter(!is.na(genetic.held)) %>% mutate(Species=gsub('_', ' ', Species))
curr.DF2 <- env.surrogate.spp.DF %>% filter(!is.na(r2CU)) %>% mutate(Species=gsub('_', ' ', Species))
curr.DF2$R2_repr <- round(curr.DF2$r2CU,2)
curr.DF2$R2_repr <- sapply(curr.DF2$R2_repr, function(x) {as.character(as.expression(substitute(~~italic(R)^2~"="~r2, list(r2=x))))})
curr.DF2$surrogate.held <- 0
curr.DF2$genetic.held <- 0.9

# make plot
suppressWarnings(
	ggplot(aes(x=surrogate.held, y=genetic.held), data=curr.DF) +
		theme_classic() +
		theme(strip.background=element_rect(fill='grey20'), strip.text=element_text(color='white', face='italic', size=12),
			panel.margin.x=unit(1, 'lines')) +
		xlab('Environmental variation secured (%)') +
		ylab('Adaptive genetic variation secured (%)') +
		geom_point(fill='transparent') +
		suppressWarnings(stat_smooth(method='glm', method.args=list(family='binomial'), fullrange=TRUE,
			se=FALSE, fill='blue', alpha=0.8)) +
		geom_text(aes(label=R2_repr), data=curr.DF2, parse=TRUE, hjust=0, size=8, color='darkred') +
		facet_wrap(~ Species, ncol=4)
)
```

>>>>

```{r, include=FALSE}
# load .rda file
checkpoint::checkpoint('2016-08-03', R.version='3.3.1', scanForPackages=FALSE)
try(session::restore.session('data/final/results.rda'))

@@

```{r, fig.width=15, fig.height=3, fig.cap='Climatic variation. Each panel depicts variation based on a different principle component (PC). Squares represent planning units. The color of each planning unit denotes the average PC value of pixels inside it. Planning units with more similar colors have more similar climate regimes.', echo=FALSE}
do.call(
	grid.arrange,
		append(
		llply(grep('^env\\_.*$', names(grid.DF), value=TRUE), function(x) {
			grid.FPLY$plot_title <- paste0('PC ', substr(x, nchar(x), nchar(x)))
			ggplot() +
				geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
					fill='grey85', color='grey70') +
				geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
					group='group', fill=x), color='grey10') +
				theme_classic() +
				theme(
					axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
					panel.border=element_rect(color='black', fill=NA, size=1),
					strip.background = element_rect(fill='grey20'),
					strip.text = element_text(color='white', size=11)
				) +
				coord_cartesian(
					xlim=buffered.range(grid.FPLY$long, 0),
					ylim=buffered.range(grid.FPLY$lat, 0)
				) +
				scale_fill_gradientn(name='',
					colors=brewer.pal(9, 'RdYlBu'),
					guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
				) +
				facet_wrap(~ plot_title)
		}),
		list(ncol=4)
	)
)
```

@@

```{r, echo=FALSE, include=FALSE}
plot.spp.nmds <- function(i) {
	## prepare data
	# get vector of adaptive and neutral column names
	adapt.col <- grep(
		paste0(unique(spp.samples.DF$species)[i], '_adaptive_d'),
		names(grid.FPLY), value=TRUE, fixed=TRUE
	)
	neutral.col <- grep(
		paste0(unique(spp.samples.DF$species)[i], '_neutral_d'),
		names(grid.FPLY), value=TRUE, fixed=TRUE
	)
	# skip species if not used in analysis
	curr.FPLY <- grid.FPLY[,
		c(adapt.col, neutral.col,
		'long','lat','group'),drop=FALSE]
	curr.FPLY <- curr.FPLY[which(!is.na(curr.FPLY[[1]])),]
	curr.FPLY <- curr.FPLY %>% gather(d, value, contains('adaptive'), contains('neutral')) %>% mutate(
		d=gsub(paste0(unique(spp.samples.DF$species)[i], '_'), '', d, fixed=TRUE),
		d=gsub('_', ' ', d, fixed=TRUE)
	)
	for (j in seq_len(length(adapt.col)+length(neutral.col)))
		curr.FPLY[['d']] <- gsub(as.character(j), paste0('(', j, ')'), curr.FPLY[['d']], fixed=TRUE)
	curr.FPLY <- curr.FPLY %>% mutate(d=factor(gsub(' d(', ' (', d, fixed=TRUE)))
	# make plot
	curr.GROBS <- llply(unique(curr.FPLY$d), function(x) {
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey85', color='grey70') +
			geom_polygon(data=filter(curr.FPLY, d==x), aes_string(x='long', y='lat', 
				group='group', fill='value'), color='grey10') +
			theme_classic() +
			theme(
				axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
				panel.border=element_rect(color='black', fill=NA, size=1),
				strip.background = element_rect(fill='grey20'), strip.text = element_text(color='white', size=20)
			) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0),
				ylim=buffered.range(grid.FPLY$lat, 0)
			) +
			scale_fill_gradientn(name='',
				colors=brewer.pal(9, 'RdYlBu'),
				guide=guide_colorbar(ticks=element_line(color='black'),
					border=element_line(color='black'), barheight=unit(3.0, 'cm'))
			) + facet_wrap(~d)
	})
	do.call(grid.arrange, append(curr.GROBS, list(ncol=3)))
	invisible()
}

calc.fig.height <- function(i) {
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	n.plots <- 0 
	# count adaptive plot
	if (adapt.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
	# count neutral plot
	if (neutral.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
	# exports
	if (n.plots >= 3) return((((n.plots-1) %/% 3)+1) * 2)
	return(1.85)
}

calc.fig.width <- function(i) {
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	n.plots <- 0 
	# count adaptive plot
	if (adapt.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
	# count neutral plot
	if (neutral.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
	# exports
	if (n.plots >= 3) return(10)
	return(4 * n.plots)
}

@@

```{r, echo=FALSE, fig.width=calc.fig.width(1), fig.height=calc.fig.height(1), fig.width=calc.fig.width(1), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each panel shows a different dimension of the variation as indicated by its title. Squares represent planning units. The color of each planning unit panel corresponds to the average ordinated values associated with individuals sampled inside it. No indiviudals of this species were found inside the gray planning units.')}
if (is.speciesPlottable(1)) plot.spp.nmds(1)
 ```

```{r, echo=FALSE, fig.width=calc.fig.width(2), fig.height=calc.fig.height(2), fig.width=calc.fig.width(2), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(2)) plot.spp.nmds(2)
```

```{r, echo=FALSE, fig.width=calc.fig.width(3), fig.height=calc.fig.height(3), fig.width=calc.fig.width(3), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(3)) plot.spp.nmds(3)
```

```{r, echo=FALSE, fig.width=calc.fig.width(4), fig.height=calc.fig.height(4), fig.width=calc.fig.width(4), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(4)) plot.spp.nmds(4)
```

```{r, echo=FALSE, fig.width=calc.fig.width(5), fig.height=calc.fig.height(5), fig.width=calc.fig.width(5), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(5)) plot.spp.nmds(5)
```

```{r, echo=FALSE, fig.width=calc.fig.width(6), fig.height=calc.fig.height(6), fig.width=calc.fig.width(6), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(6)) plot.spp.nmds(6)
```

```{r, echo=FALSE, fig.width=calc.fig.width(7), fig.height=calc.fig.height(7), fig.width=calc.fig.width(7), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(7)) plot.spp.nmds(7)
```

```{r, echo=FALSE, fig.width=calc.fig.width(8), fig.height=calc.fig.height(8), fig.width=calc.fig.width(8), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(8)) plot.spp.nmds(8)
```

```{r, echo=FALSE, fig.width=calc.fig.width(9), fig.height=calc.fig.height(9), fig.width=calc.fig.width(9), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(9)) plot.spp.nmds(9)
```

```{r, echo=FALSE, fig.width=calc.fig.width(10), fig.height=calc.fig.height(10), fig.width=calc.fig.width(10), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(10)) plot.spp.nmds(10)
```

```{r, echo=FALSE, fig.width=calc.fig.width(11), fig.height=calc.fig.height(11), fig.width=calc.fig.width(11), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(11)) plot.spp.nmds(11)
```

```{r, echo=FALSE, fig.width=calc.fig.width(12), fig.height=calc.fig.height(12), fig.width=calc.fig.width(12), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(12)) plot.spp.nmds(12)
```

```{r, echo=FALSE, fig.width=calc.fig.width(13), fig.height=calc.fig.height(13), fig.width=calc.fig.width(13), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(13)) plot.spp.nmds(13)
```

```{r, echo=FALSE, fig.width=calc.fig.width(14), fig.height=calc.fig.height(14), fig.width=calc.fig.width(14), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(14)) plot.spp.nmds(14)
```

```{r, echo=FALSE, fig.width=calc.fig.width(15), fig.height=calc.fig.height(15), fig.width=calc.fig.width(15), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(15)) plot.spp.nmds(15)
```

```{r, echo=FALSE, fig.width=calc.fig.width(16), fig.height=calc.fig.height(16), fig.width=calc.fig.width(16), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(16)) plot.spp.nmds(16)
```

```{r, echo=FALSE, fig.width=calc.fig.width(17), fig.height=calc.fig.height(17), fig.width=calc.fig.width(17), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(17)) plot.spp.nmds(17)
```

```{r, echo=FALSE, fig.width=calc.fig.width(18), fig.height=calc.fig.height(18), fig.width=calc.fig.width(18), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(18)) plot.spp.nmds(18)
```

```{r, echo=FALSE, fig.width=calc.fig.width(19), fig.height=calc.fig.height(19), fig.width=calc.fig.width(19), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(19)) plot.spp.nmds(19)
```

```{r, echo=FALSE, fig.width=calc.fig.width(20), fig.height=calc.fig.height(20), fig.width=calc.fig.width(20), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(20)) plot.spp.nmds(20)
```

```{r, echo=FALSE, fig.width=calc.fig.width(21), fig.height=calc.fig.height(21), fig.width=calc.fig.width(21), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(21)) plot.spp.nmds(21)
```

```{r, echo=FALSE, fig.width=calc.fig.width(22), fig.height=calc.fig.height(22), fig.width=calc.fig.width(22), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(22)) plot.spp.nmds(22)
```

```{r, echo=FALSE, fig.width=calc.fig.width(23), fig.height=calc.fig.height(23), fig.width=calc.fig.width(23), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(23)) plot.spp.nmds(23)
```

```{r, echo=FALSE, fig.width=calc.fig.width(24), fig.height=calc.fig.height(24), fig.width=calc.fig.width(24), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(24)) plot.spp.nmds(24)
```

```{r, echo=FALSE, fig.width=calc.fig.width(25), fig.height=calc.fig.height(25), fig.width=calc.fig.width(25), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(25)) plot.spp.nmds(25)
```

```{r, echo=FALSE, fig.width=calc.fig.width(26), fig.height=calc.fig.height(26), fig.width=calc.fig.width(26), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(26)) plot.spp.nmds(26)
```

```{r, echo=FALSE, fig.width=calc.fig.width(27), fig.height=calc.fig.height(27), fig.width=calc.fig.width(27), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S29 caption for conventions.')}
if (is.speciesPlottable(27)) plot.spp.nmds(27)
```
